---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
To go back to my progress report...   
[link to the README.md of hw09](https://github.com/bcahn7/STAT547M-hw-An-Byeongchan/blob/master/hw09/README.md)  




```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# powers

This is an R package that provides power functions.
The goal of powers is to make it easier to calculate power functions.

## Installation
You can install powers from github with:
```{r}
# install.packages("devtools")
devtools::install_github("bcahn7/STAT547M-hw09-powers")
```


## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
powers::cube(3)
powers::reciprocal(1:5)
```
It has additional function to print out a scatter plot! The default value for the argument `plot_it` is `FALSE`.
```{r}
## printing out a scatter plot!
powers::square(1:5, plot_it = TRUE)
powers::reciprocal(1:10, plot_it = TRUE)
```
In addition, it has an argument for `na.omit`. This is an option to remove `NA`s from an input vector. The default value is `FALSE`.
```{r}
powers::cube(c(1,2,3, NA, 5, 6, NA, 8), plot_it = FALSE, na.omit = TRUE)
powers::four(c(1,2,3, NA, NA ,NA), na.omit = TRUE)
```
  
   
This `powers` package also has a `boxcoxt` function which print out the one-parameter Box-Cox transformation.     
This function does not calculate the optimal lambda value. Using `boxcox()` in the `MASS` package is recommended for the optimal lambda. The default value of lambda is 0.1
```{r}
powers::boxcoxt(5:10)
powers::boxcoxt(1:10, lambda = 0.3)
```
When the input lambda is too big(>5) or too small(<-5), there's a `warning`: "The input lambda value is too big or too small".
```{r}
powers::boxcoxt(1:10, lambda = 9)
```
     
   
   
For convenience, there are two datasets in `powers` package. Those datasets are `1:10`, `-(1:10)`
```{r}
powers::tenvec
powers::negtenvec
```





## For Developers
Use the internal `pow` function as the machinery for the front-end functions such as `square`, `cube`, `four`, and `reciprocal`.

