---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# powers

This is an R package that provides power functions.
The goal of powers is to make it easier to calculate power functions.

## Installation
You can install powers from github with:
```{r}
# install.packages("devtools")
devtools::install_github("bcahn7/STAT547M-hw09-An-Byeongchan/STAT547M-hw09-powers")
```


## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
powers::cube(3)
powers::reciprocal(1:5)
```
It has additional function to print out a scatter plot! Default value for the argument `plot_it` is `FALSE`.
```{r}
## printing out a scatter plot!
powers::square(1:5, plot_it = TRUE)
powers::reciprocal(1:10, plot_it = TRUE)
```

## For Developers
Use the internal `pow` function as the machinery for the front-end functions such as `square`, `cube`, `four`, and `reciprocal`.

