---
title: "Vignette for powers"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

**Note**: This package isn't actually meant to be "serious". This is a practice for STAT547M hw09. 
  
    
This `powers` package makes it possible to calculate square, cube, the fourth power, and reciprocal and print out a corresponding scatter plot.

```{r}
library(powers)
```
Want squares, cubes, the fourth powers, or reciprocal? Easy.
```{r}
square(1:10)
cube(1:10)
reciprocal(5:10)
```
`apply`-family friendly, too!
```{r}
my_list <- list(1:10, 0.5, -0.7)
## So base-R-boring!
lapply(my_list, function(x) x^2)
## Use powers instead!
lapply(my_list, square)
```
It has additional function to print out a scatter plot! The default value for the argument `plot_it` is `FALSE`.
```{r}
reciprocal(1:10, plot_it = TRUE)
square(1:10, plot_it = TRUE)
```
In addition, it has an argument for `na.omit`. This is an option to remove `NA`s from an input vector. The default value is `FALSE`.
```{r}
cube(c(1,2,3, NA, 5, 6, NA, 8), plot_it = FALSE, na.omit = TRUE)
four(c(1,2,3, NA, NA ,NA), na.omit = TRUE)
```
  
   
This `powers` package also has a `boxcoxt` function which print out the one-parameter Box-Cox transformation.     
This function does not calculate the optimal lambda value. Using `boxcox()` in the `MASS` package is recommended for the optimal lambda. The default value of lambda is 0.1
```{r}
boxcoxt(1:10, lambda = 0.3)
```
  
  
  
For convenience, there are two datasets in `powers` package. Those datasets are `1:10`, `-(1:10)`
```{r}
tenvec
negtenvec
```



